Appendix S2: Data Exploration

### 2022-04-28 ms/data_readme.Rmd
Update data README
Add DOIs

Recommended citation for the data: Nitta JH, Mishler BD, Iwasaki W, Ebihara A
(2022) Data from: Spatial phylogenetics of Japanese ferns: Patterns, processes,
and implications for conservation FIXME: add DOI when available

Citation for and links to publications that cite or use the data: Nitta JH,
Mishler BD, Iwasaki W, Ebihara A (2022) Spatial phylogenetics of Japanese ferns:
Patterns, processes, and implications for conservation.
American Journal of Botany. FIXME: add DOI, page numbers when available

@@

- doi_10.5061_dryad.4362p32__v4.zip: Data including DNA sequences, taxonomy, and 
breeding system data for native Japanese ferns [@Ebihara2019b] downloaded from 
https://datadryad.org/stash/dataset/doi:10.5061/dryad.4362p32. 
MD5 checksum `r tools::md5sum(here::here(ebihara_2019_zip_file))`
- ftol_data_release_v0.0.1.zip: Fern Tree of Life project global DNA alignment 
and phylogenetic tree (Nitta et al., in prep.) downloaded from 
https://figshare.com/s/87b8ec102303bf9f3212.
MD5 checksum `r tools::md5sum(here::here(ftol_zip_file))`
FIXME: replace with DOI when available

@@

For full methods, see Nitta JH, Mishler BD, Iwasaki W, Ebihara A (2022) Spatial
phylogenetics of Japanese ferns: Patterns, processes, and implications for
conservation. American Journal of Botany. 
FIXME: add DOI, page numbers when available

>>>>

Recommended citation for the data: Nitta JH, Mishler BD, Iwasaki W, Ebihara A
(2022) Data from: Spatial phylogenetics of Japanese ferns: Patterns, processes,
and implications for conservation. FigShare. 
http://doi.org/10.6084/m9.figshare.16655263

Citation for and links to publications that cite or use the data: Nitta JH,
Mishler BD, Iwasaki W, Ebihara A (2022) Spatial phylogenetics of Japanese ferns:
Patterns, processes, and implications for conservation.
American Journal of Botany. https://doi.org/10.1002/ajb2.1848

@@

- doi_10.5061_dryad.4362p32__v4.zip: Data including DNA sequences, taxonomy, and 
breeding system data for native Japanese ferns [@Ebihara2019b] downloaded from 
https://datadryad.org/stash/dataset/doi:10.5061/dryad.4362p32. 
MD5 checksum `r tools::md5sum(here::here(ebihara_2019_zip_file))`
- ftol_data_release_v0.0.1.zip: Fern Tree of Life (FTOL) project global DNA 
alignment and phylogenetic tree v0.0.1 (Nitta et al., in prep 
https://doi.org/10.1101/2022.03.31.486640) downloaded from 
https://doi.org/10.6084/m9.figshare.13251290.v1.
MD5 checksum `r tools::md5sum(here::here(ftol_zip_file))`

@@

For full methods, see Nitta JH, Mishler BD, Iwasaki W, Ebihara A (2022) Spatial
phylogenetics of Japanese ferns: Patterns, processes, and implications for
conservation. American Journal of Botany. https://doi.org/10.1002/ajb2.1848
